Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-01-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates abstract
update conclusion
updates

Studying the viscous fingering patterns as a function of viscosity ratio along with the initial and boundary conditions, as well as implement adaptivity on top of an unstructured mesh will allow the user to directly apply and setup a geological model accurately and without the need of upscaling. Properties such as porosity and adaptivity can be easily introduced in the model while the idea of the preferential flow bath can be distinguished from the finger formation mechanics, in particular the tip-splitting finger behaviour.

@@

>>>>

Studying the viscous fingering patterns as a function of viscosity ratio along with the initial and boundary conditions, as well as implement adaptivity on top of an unstructured mesh will allow the user to directly apply and setup a geological model accurately and without the need of upscaling. Properties such as porosity and adaptivity can be easily introduced in the model while the idea of the preferential flow path can be distinguished from the finger formation mechanics, in particular the tip-splitting finger behaviour.

@@

\medskip
A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs (Fig.~\ref{3DChannel_satvel_XYplanes_adapt}a). Distinct preferable flow pathways can be shown (Fig. \ref{3DChannel_satvel_XYplanes_adapt}c)
%(Fig.~\ref{fig:3DChannel_severalfields_adapt}c)
, in particular through the central channel (see streamlines in 
Fig. \ref{3DChannel_satvel_XYplanes_adapt}f)
%Fig.~\ref{fig:3DChannel_severalfields_adapt}b) 
and at the top of the domain.
